\textls[-0]{\thetitle}

### 2023-03-24 canonicitymodel.tex
tweak

Like most logical-relations proofs, we interpret each judgment and inductively
interpret each syntax piece. We are working in an intrinsic setting; thus, even if
we omit contexts for brevity, the syntax piece is still well-typed. However,
unlike most logical-relations proofs, our logical-relations model is proof-relevant,
which is essential for modeling universes
properly~\cite{coquand2018canonicity}.
Our canonicity model for the base MLTT fragment is following the ones
in \citet{coquand2018canonicity} and \citet{sterling2019algebraic} in that it
utilizes the facilitates of the ambient meta\-logic; for example, we use dependent functions and
dependent tuples in the ambient meta\-logic to model dependent functions and tuples in \TT.
% We will omit the treatment of the universe and the verification of most equality for simplicity (and the treatment of the universe will not affect our model). Interested audience can refer to \citet{kaposi2019gluing, coquand2018canonicity,sterling2019algebraic} for a complete technical treatements.

>>>>

Like most logical-relations proofs, we interpret each judgment and inductively
interpret each syntax piece. We are working in an intrinsic setting; thus, even if
we omit contexts for brevity, the syntax piece is still well-typed. However,
unlike most logical-relations proofs, our logical-relations model is proof-relevant,
which is essential for modeling universes
properly~\cite{coquand2018canonicity}.
Our canonicity model for the base MLTT fragment follows the constructions
in \citet{coquand2018canonicity} and \citet{sterling2019algebraic} in that it
utilizes the facilitates of the ambient meta\-logic; for example, we use dependent functions and
dependent tuples in the ambient meta\-logic to model dependent functions and tuples in \TT.
% We will omit the treatment of the universe and the verification of most equality for simplicity (and the treatment of the universe will not affect our model). Interested audience can refer to \citet{kaposi2019gluing, coquand2018canonicity,sterling2019algebraic} for a complete technical treatements.
